### 2016-03-29 paper.tex
change png to eps
add conclusion

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=8cm,height=6cm]{Rate_all.png}
			\figcaption{\label{fig2}
				Dark noise event rate with different trigger time window
			}
		\end{center}

@@

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=8cm,height=6cm]{4MeV_e+_PMT_first_hitTime_all.png}
			\figcaption{\label{fig2}   PMT's first hit time with different situations 
			}
		\end{center}

@@

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{C14_deltaR_new.png}
			\figcaption{\label{fig2}   Delta of true C14 event vertex and reconstructed approximate event vertex}
		\end{center}

@@

		To take the numbers in table 1 as the inputs of simulations, events rate from background are estimated again with new trigger scheme. 
		The events rate from different radioactivity sources are summed up and the results are listed in table 2 with different trigger threshold and in
		different fiducial volumes.

@@

		\section{Estimation of data volume in JUNO}
		JUNO is proposed to run at least 6 years for neutrino mass hiarachy measurements and other physics topics. 
		It's important for offline data processing and disk storage preparation to estimate the data volume after 6 years running. 
		Different events have different event size, depending on number of photo-electrons detected by CD.
		Fig. ?? shows the PE numbers from different event sources, including radioactivity events and different physical events.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The DAQ data rate of central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  DAQ data rate(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m &400.598  &317.369  &315.246  &313.138  &311.188  &309.020  \\  
			R$<$11m &424.110  &319.089  &316.580  &314.189  &312.013  &309.234  \\
			R$<$12m &518.613  &325.933  &321.949  &318.466  &315.418  &310.087  \\
			R$<$13m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$14m &621.595  &332.270  &326.988  &322.522  &318.662  &310.880  \\
			R$<$15m &703.853  &347.291  &337.170  &329.547  &323.657  &312.730  \\
			R$<$16m &1049.85  &425.088  &388.524  &363.975  &347.654  &322.219  \\
			R$<$17m &1219.60  &476.504  &421.716  &385.604  &362.360  &328.461  \\

@@

		If electronic system can't do waveform compression, we need do waveform compression in DAQ system and
		then save the data to disk. With the waveform compression for low energy events, we can 
		shorten the waveform  length from
		1 $\mu$s to 50ns. So each low energy event contributes 0.1MBytes data, the estimated disk storage
		space is listed in table.4.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The disk storage space of central detector on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  disk storage space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m  &122.630  &118.468  &118.362  &118.257  &118.159  &118.051 \\  
			R$<$11m  &123.806  &118.554  &118.429  &118.309  &118.201  &118.062 \\
			R$<$12m  &128.531  &118.897  &118.697  &118.523  &118.371  &118.104 \\
			R$<$13m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$14m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$15m  &137.793  &119.965  &119.459  &119.077  &118.783  &118.236 \\
			R$<$16m  &155.092  &123.854  &122.026  &120.799  &119.983  &118.711 \\
			R$<$17m  &163.580  &126.425  &123.686  &121.880  &120.718  &119.023 \\

		\section{Conclusion}
		\vspace{-1mm}
		\centerline{\rule{80mm}{0.1pt}}
		\vspace{2mm}

>>>>

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=8cm,height=6cm]{Rate_all.eps}
			\figcaption{\label{fig2}
				Dark noise event rate with different trigger time window
			}
		\end{center}

@@

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=8cm,height=6cm]{4MeV_e+_PMT_first_hitTime_all.eps}
			\figcaption{\label{fig2}   PMT's first hit time with different situations 
			}
		\end{center}

@@

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{C14_deltaR_new.eps}
			\figcaption{\label{fig2}   Delta of true C14 event vertex and reconstructed approximate event vertex}
		\end{center}

@@

		To take the numbers in table 1 as the inputs of simulations, events rate from background are estimated again with new trigger scheme. 
		The events rate from different radioactivity sources are summed up and the results are listed in table 5 with different trigger threshold and in
		different fiducial volumes.

@@

		\section{Estimation of data volume in JUNO}
		JUNO is proposed to run at least 6 years for neutrino mass hiarachy measurements and other physics topics. 
		It's important for offline data processing and disk storage preparation to estimate the data volume after 6 years running. 
		Different events have different event size, depending on number of photo-electrons detected by CD.
		The data volume of physical events excepting muon events and supernova events can be negligible comparing with radioactivity events. 
		Fig.5  shows the fired PMT number distributions from different radioactivity events on each detector material.

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{distribution_of_fired_PMTNum.eps}
			\figcaption{\label{fig2}   Distributions of fired PMT number on different materials}
		\end{center}

		With this distributions, we can estimate the data volume of different materials' radioactivity events.

		In JUNO electronic system for low energy radioactivity events the assuming sampling time window is 1 $\mu$s. Each sampling point contribute 2 bytes data, so each low energy event contribute 2 MBytes data. The estimated data volume about radioactivity events of CD on different energy and radius threshold is listed in table 6.

	\end{multicols}
	\begin{center}
		\tabcaption{ \label{tab1} The data volume of central detector radioactivity events on different energy and radius threshold }
		\footnotesize
		\begin{tabular*}{170mm}{@{\extracolsep{\fill}} c c c c c c c}
			\toprule  disk storage space(MBytes/s)&E$>$0.1MeV & E$>$0.2MeV & E$>$0.3MeV & E$>$0.4MeV & E$>$0.5MeV & E$>$0.6MeV \\
			\hline
			R$<$10m  &122.630  &118.468  &118.362  &118.257  &118.159  &118.051 \\  
			R$<$11m  &123.806  &118.554  &118.429  &118.309  &118.201  &118.062 \\
			R$<$12m  &128.531  &118.897  &118.697  &118.523  &118.371  &118.104 \\
			R$<$13m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$14m  &133.680  &119.213  &118.949  &118.726  &118.533  &118.144 \\
			R$<$15m  &137.793  &119.965  &119.459  &119.077  &118.783  &118.236 \\
			R$<$16m  &155.092  &123.854  &122.026  &120.799  &119.983  &118.711 \\
			R$<$17m  &163.580  &126.425  &123.686  &121.880  &120.718  &119.023 \\

@@

		For the high energy muon events and supernova events, all the PMTs will be fired. We assume
		the total PMT number of CD is about 18000, so each muon and supernova event contribute 36 MBytes.
		The event rate of muon is about 3Hz, so the data volume of muon events is about 100MBytes/s .

		\section{Conclusion}
		The total events rate from physical channel excepting supernova event in JUNO is less 
		than 1 Hz. So the data volume of physical events excepting supernova event is negligible 
		comparing with those from radioactity backgrounds. With
		a typical energy threshold 0.5MeV , the data volume of radioactity
		backgrounds is about ??? MBytes/s. The data volume of muon events is about 100MBytes/s.

		With a more sophisticated trigger scheme, the energy threshold can be reduced to 0.2MeV which 
		is preferred by solar neutrinos and supernova neutrinos study. With 0.2MeV energy threshold and
		17m radius threshold the data volume of radioactity backgrounds is about ??? MBytes/s. Table.6
		show the data volume of central detector radioactivity events on different energy and radius 
		threshold.

		The rescults of the present study provide important event rates estimation and trigger scheme 
		for JUNO design and disk storage preparation.

		\vspace{-1mm}
		\centerline{\rule{80mm}{0.1pt}}
		\vspace{2mm}
